\documentclass{article}
\usepackage[utf8]{inputenc}

\title{Deep Learning- Final Course Project}
\author{Arye Amsalem (ID. 123456789),Miri Yungreis ID. 987654321)}
\date{Submitted as final project report for the DL course, BIU, 2021}

\usepackage{natbib}
\usepackage{graphicx}
\usepackage{hyperref}

\begin{document}

\maketitle

\section{Introduction}

Provide some background for the project. give some overall motivation.

\subsection{Related Works}
Please provide some references to existing works, if you found any. it's an optional sub section, but can definitely help.



\section{Solution}
\subsection{General approach}
Describe your preferred approach to solve the problem. what alternatives you plan to try and why.

\subsection{Design}
Provide some general information about your code, platform, how long it took you to train it, technical challenges you had, Loss functions, Optimizers, Architecture, and more.

\section{Experimental results}
Provide information about your experimental settings. What alternatives did you measure? Make sure this part is clear to understand, provide as much details as possible. Provide results with tables and figures.

\section{Discussion}
Provide some final words and summarize what you have found from running the experiments you described above. Provide some high level insights.

Note - your project will be evaluated for aspects, including the technique you selected, the rational of the experiments you decided to run, the insights you learned from this process and more. Remember, for the purpose of this course, the process that you demonstrate is very  important.

\section{Code}
this is the link to our github repository:

\url{https://github.com/Arye182/Deep_Learning_Monet_Competition_Kaggle}

%%%%%%%%%%% bibliography %%%%%%%%%%%%%%%%%%%%%%%%%%
\bibliographystyle{plain}
\bibliography{references}
\begin{thebibliography}{100}
\bibitem{1 - CycleGan Article} https://arxiv.org/pdf/1703.10593.pdf
\bibitem{2 - CycleGan Documentation}https://www.tensorflow.org/tutorials/generative/cyclegan
\bibitem{3 - CycleGan Implementation} https://www.youtube.com/watch?v=4LktBHGCNfw
\end{thebibliography}
%%%%%%%%%% end bibliography %%%%%%%%%%%%%%%%%%%%%%%
\end{document}